\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-24 main.tex
Updates from Overleaf

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{examples/images/inductance.pdf}
    \caption{Self-inductance $L$ of a circular ring with inner radius $a$ and outer radius $b$, as a function of the ratio $a / b$ and the ring's effective penetration depth $\Lambda$. Filled circles indicate results from \SuperScreen, solid lines show numerical results from Ref.~\cite{Brandt2004-ew} (Figure 2), blue squares and diamonds show numerical results from Ref.~\cite{Khapaev_1997} (Figure 1), and the dashed line indicates the analytical solution, $L = 2\mu_0 a$, for $\Lambda=0$ in the limit $a/b\to 0$\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}.}
    \label{fig:inductance}
\end{figure}
